Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-12 aistats.tex
Format optimization summary table

@@

\begin{table*}[t]\begingroup
\renewcommand*{\arraystretch}{1.25}%
\centering
\begin{tabular}{p{.35\textwidth}p{.6\textwidth}}
\toprule
Assumption &  \\
\midrule
%Strongly convex and bounded variance\newline
%\citep[e.g.,][]{??}
%&
%$
%\cB_A(\theta,\theta') \geq \frac{1}{2}\norm{\theta-\theta'}^2,
%\quad
%\expect[x]{\norm{\m - x}}^2\leq\sigma^2
%$
%\\
Uniformly bounded ``variance''\newline
\citep{hanzely2018fastest}
&
	$
	\expect[x]{
	\begin{aligned}
	\cB_{A^*}\paren{(1-\eta) \m + \eta x, (1-\eta)\m + \eta \m_*}\\
	+\, \cB_{A^*}\paren{(1-\eta)\m + \eta \m_*, (1-\eta) \m + \eta x}
	\end{aligned}
	}
	\leq
	\eta^2 C
	$
\\
Bounded ``variance'' at $\theta_*$\newline
\citep{dragomir2021fast}
&
	$\expect[x]{
		\cB_{A^*}(\m - 2\eta (\m_* - x), \m)
	} \leq 2 \eta^2 C$
\\
Bounded optimality gap\newline
\citep{dorazio2021stochastic}
&
?
\\
\bottomrule
\end{tabular}
\caption{Caption}
\label{tbl:assumptions}
\endgroup\end{table*}

>>>>

\usepackage{array}

@@

\begin{table}[t]
\begingroup
\renewcommand*{\arraystretch}{1.25}%
\newcommand*{\greencmark}{\textcolor{Green}{\cmark}}
\newcommand*{\redxmark}{\textcolor{Red}{\xmark}}
\centering
\begin{tabular}{lccc}
%{p{.15\textwidth}m{.05\textwidth}m{.08\textwidth}m{.1\textwidth}}
\toprule
Boundedness & Barrier &  $\lr_n \sim \inv{n}$ & Last iterate \\
\midrule
%Strongly convex and bounded variance\newline
%\citep[e.g.,][]{??}
%&
%$
%\cB_A(\theta,\theta') \geq \frac{1}{2}\norm{\theta-\theta'}^2,
%\quad
%\expect[x]{\norm{\m - x}}^2\leq\sigma^2
%$
%\\
Variance on all $\Theta$ % \newline \citep{hanzely2018fastest}
& \redxmark & \greencmark  & \redxmark
\\
Variance at $\theta_*$ %\newline \citep{dragomir2021fast}
& \redxmark & \greencmark  & \greencmark
\\
Optimality gap %\newline \citep{dorazio2021stochastic}
& \greencmark & \redxmark & \greencmark
\\
\bottomrule
\end{tabular}
\caption{
Summary of results about SMD with relative smoothness and relative strong convexity assumptions. 
Barrier tells whether the assumption can hold with barrier objectives.
$\lr_n \sim \inv{n}$ says whether the convergence rate hold with this step-size scheduling, and the last column tells whether the rate applies to the last iterate or to some average iterate.
}
\label{tbl:assumptions}
\endgroup
\end{table}
